\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliograf\'ia}

\bibitem{adameHamilt}
  L.~E.~Adame, L.~M.~Rivera y A.~L.~Trujillo-Negrete,
  \textit{Hamiltonicity of Token Graphs of Some Join Graphs},
  Symmetry 13 (2021) 1076. 

\bibitem{alaviDVGraphs}
  Y.~Alavi, M.~Behzad, P.~Erdos y D.~R.~Lick,
  \textit{Double vertex graphs},
  Journal of Combinatorics, Information and System Sciences 16 (1991) 37--50.

\bibitem{alaviPlanarity}
  Y.~Alavi, M.~Behzad y J.~E.~Simpson,
  \textit{Planarity of double vertex graphs},
  Graph Theory, Combinatorics, Algorithms, and Applications (1991) 472--485.

\bibitem{alaviHamilt}
  Y.~Alavi, D.~R.~Lick y J.~Liu,
  \textit{Hamiltonian cycles in double vertex graphs of bipartite graphs},
  Congressus Numerantium 93 (1993) 65--72.

\bibitem{alzagaSymPower}
  A.~Alzaga, R.~Iglesias y  R.~Pignol,
  \textit{Spectra of symmetric powers of graphs and the Weisfeiler-Lehman
  refinements},
  Journal of Combinatorial Theory, Series B (2010) 100(6) 671--682. 

\bibitem{audeanetSymPower}
  K.~Audenaert, C.~Godsil, G.~Royle y T.~Rudolph,
  \textit{Symmetric squares of graphs},
  Journal of Combinatorial Theory, Series B 97 (2007) 74--90. 

\bibitem{barghi-ponomarenko}
  A.~R.~Barghi y I.~Ponomarenko,
  \textit{Non-isomorphic graphs with cospectral symmetric powers},
  The Electronic Journal of Combinatorics 16(1) (2009) R120.

\bibitem{bondy2008}
  J.~A.~Bondy y U.~S.~R.~Murty,
  \textbf{Graph Theory},
  Springer, 2008.

\bibitem{carballosaRegPlan}
  W.~Carballosa, R.~Fabila-Monroy, J.~Lea\~{n}os y L.~M.~Rivera,
  \textit{Regularity and planarity of token graphs},
  Discussiones Mathematicae Graph Theory (2017) 37(3) 573--586. 

\bibitem{diestel2017}
  R.~Diestel,
  \textbf{Graph Theory, Fifth Edition},
  Springer, 2017.

\bibitem{fabilaToken}
  R.~Fabila-Monroy, D.~Flores-Pe\~{n}aloza, C.~Huemer, F.~Hurtado, J.~Urrutia y
  D.R.~Wood,
  \textit{Token graphs},
  Graphs and Combinatorics 28(3) (2012) 365--380. 
  
\bibitem{leaEConnect}
  J.~Lea\~{n}os y M.~K.~Ndjatchi,
  \textit{The edge-connectivity of token graphs},
  Graph Combinator 37 (2021) 1013--1023. 

\bibitem{leaConnect}
  J.~Lea\~{n}os y A.~L.~Trujillo-Negrete,
  \textit{The connectivity of token graphs},
  Graphs and Combinatorics 34 (2018) 777--790. 
 
\bibitem{riveraHamilt}
  L.~M.~Rivera y A.~L.~Trujillo-Negrete,
  \textit{Hamiltonicity of token graphs of fan graphs},
  Art of Discrete and Applied Mathematics 1 (2018) \#P07. 

\bibitem{rudolphGInv}
  T.~Rudolph,
  \textit{Constructing physically intuitive graph invariants},
  arXiv:quant-ph/0206068 (2002).

\bibitem{zhuConnect}
  B.~Zhu, D.~R.~Lick, J.~Liu y Y.~Alavi,
  \textit{Connectivity relationships between a graph and its double vertex
  graphs},
  Bull. ICA 12 (1994) 23--27.

\bibitem{zhuNTuples}
  B.~Zhu, J.~Liu y D.~R.~Lick,
  \textit{n-Tuple vertex graphs},
  Congressus Numerantium 89 (1992) 97--106.


\end{thebibliography}
